An Efficient Interpolation Technique for Jump Proposals in Reversible-Jump Markov Chain Monte Carlo Calculations

### 2011-03-17 paper.tex
GitHub address and acknowledgements for WMF.

We have made our implementation of the technique described in this paper publicly available online at \will{URL}, and welcome readers to take advantage of this toolkit.

@@

We are grateful to Neil Cornish for interesting discussions.  IM acknowledges support from the NSF Astronomy and Astrophysics Postdoctoral Fellowship, award AST-0901985.  WF acknowledges support from \will{Add your acknowledgements}

>>>>

We have made our implementation of the technique described in this
paper publicly available online at
\url{http://github.com/farr/mcmc-ocaml}, and welcome readers to take
advantage of this toolkit.

@@

We are grateful to Neil Cornish for interesting discussions.  IM
acknowledges support from the NSF Astronomy and Astrophysics
Postdoctoral Fellowship, award AST-0901985.  WF acknowledges support
from NSF grants CAREER AST-0449558 and AST0908930.
